Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-09-28 draft1.1.tex
テスト
updated 4.B, added adiabatic approximation

\usepackage{comment}
%\usepackage[dvips]{graphicx}
%\usepackage{amsmath,amssymb}
%\usepackage{mathrsfs}
%\usepackage{txfonts}
\usepackage{braket}
%\usepackage{latexsym}
%\usepackage{ascmac}
%\usepackage{fancybox}
%\usepackage{type1cm}
\usepackage{cases}
\usepackage{caption}
\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}

@@

The most common approach to the quantization of the nuclear collective model
is the canonical quantization \cite{BM75}.
In the pairing collective model, the canonical quantization
was adopted in previous studies \cite{BBPK70,delta1,delta3}.
Assuming magnitude and phase of the pairing gap as collective coordinates,
a collective Hamiltonian was constructed in the second order in momenta.
Then, the Hamiltonian was quantized by the canonical quantization
with the Pauli's prescription.
In this section, we apply similar quantization method to
the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
The main difference is that the collective canonical variables are
not assumed in the present case, but are obtained from the TDHFB dynamics
itself.
%The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation

@@

>>>>

%aaa
\usepackage{comment}
%\usepackage[dvips]{graphicx}
%\usepackage{amsmath,amssymb}
%\usepackage{mathrsfs}
%\usepackage{txfonts}
\usepackage{braket}
%\usepackage{latexsym}
%\usepackage{ascmac}
%\usepackage{fancybox}
%\usepackage{type1cm}
\usepackage{cases}
\usepackage{caption}
\usepackage[top=25truemm,bottom=20truemm,left=20truemm,right=20truemm]{geometry}

@@

The most common approach to the quantization of the nuclear collective model
is the canonical quantization \cite{BM75}.
In the pairing collective model, the canonical quantization
was adopted in previous studies \cite{BBPK70,delta1,delta3}.
Assuming magnitude and phase of the pairing gap as collective coordinates,
a collective Hamiltonian was constructed in the second order in momenta.
Then, the Hamiltonian was quantized by the canonical quantization
with the Pauli's prescription.
In this section, we apply similar quantization method to
the TDHFB Hamiltonian (\ref{TDHFB_Hamiltonian_3}).
The main difference is that the collective canonical variables are
not assumed in the present case, but are obtained from the TDHFB dynamics
itself.\par
In this section, we consider two separated methods to solve the quantum mechanics: periodic boundary condition and adiabatic approximation. 
%The most natural procedure for quantizing classical dynamics is canonical quantization. The canonical variables become to operators and fulfill the commutation relation

\subsubsection{Periodic boundary condition}

@@

\subsubsection{Adiabatic approximation}
We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
The adiabatic approximation means $\phi$ in Hamiltonian can be
 expanded up to second order
\begin{align}
 \mathcal{H}(\phi,j;J)
	\approx V(j:J) + \frac{1}{2B(j;J)}j^2
\end{align}
where
\begin{align}
 V(j:J) &\equiv \mathcal{H}(\phi=0,j;J) \nonumber \\
  &= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
- \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} \\
 B(j;J)^{-1} &\equiv \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2}\right|_{\phi=0} \nonumber \\
 &= \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} .
\end{align}
We transform the carved space into plain space
 which keeps the mass parameter equals one
\begin{align}
 \mathcal{H}(\phi,j;J) \to \mathcal{\bar{H}}(p,q;J) = \bar{V}(q;J) + \frac{1}{2}p^2 .
\end{align}
The relation between both coordinates fulfills
\begin{align}
 \frac{\partial q(j)}{\partial j} = \sqrt{B(j;J)} .
\end{align}
Instead of Pauli prescription, we solve the Schr\"{o}dinger equation in plain space
\begin{equation}
	\bar{H}\left( q,-i\frac{d}{dq},\frac{N}{2} \right)
	u_k^{(N)}(q) = E_k^{(N)}u_k^{(N)}(q).
	\label{Schroedinger_eq2}
\end{equation}
At weak pairing limit in ground state, most of the component of wave function is expected to occupy around the minimum value of $j$. We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, where $q_{min}$ corresponds to the minimum value of $j$.
